Network Configuration Synthesis with Abstract Topologies

### 2016-11-07 paper/abstraction/appendix.tex
changing proof to account for origination:

@@

  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}(PG,ord) = \{ \\
     ~~~~~ \{ l \rightarrow rc ~\vert \\
     ~~~~~~~~~ l \in internal(V) \\
     ~~~~~~~~~ m = (l,q_m) \in PG, \\
     ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
     ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\

     ~~~~~ \}
  \end{array} \]%

@@

Figure~\ref{fig:abgp-syntax} also defines the translation of the product graph $PG = (G', s, P)$ to the ABGP representation. It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.

@@

Here we define what it means to concretize an abstract \sysname policy. 
Concretization takes as input, a policy and a map $m$ from template prefix to a set of concrete prefixes.

\[ \begin{array}{rcl}
  con(\emptyset,m)                        & = & \emptyset \\
  con(l,m)                                & = & \Sigma ~ \{ l_i \in f^{-1}(l) \} \\
  con(r_1 \cup r_2,m)                     & = & con(r_1,m) \cup con(r_2,m) \\
  con(r_1 \cap r_2,m)                     & = & con(r_1,m) \cap con(r_2,m) \\
  con(!r,m)                               & = & !con(r,m) \\
  con(r^*,m)                              & = & con(r,m)^* \\
  con(pfx \Rightarrow r_1, \dots, r_n,m)  & = & pfx \Rightarrow con(r_1,m), \dots, con(r_n,m) \\
  con(\$x \Rightarrow r_1, \dots, r_n,m)  & = & \{ pfx \Rightarrow con(r_1,m), \dots, con(r_n,m) ~\vert~ {pfx} \in m(x) \} \\
\end{array} \]

For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a single entry for each of its corresponding concrete values under the supplied mapping $m$.
We can also define concretization over the ABGP policy as:

\[ \begin{array}{rcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,m) 
        & = & 
        \{ x \rightarrow con(rc_i,m)  ~\vert~ x \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,m) 
        & = &  
        \{ pfx \rightarrow con(pc_i,m) ~\vert~ pfx \in m(t_i) \}
        \\
     con(ma_1, \dots, ma_k,m) 
        & = &
        con(ma_1,m), \dots, con(ma_k,m)
        \\
     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),m) 
        & = & 
        n_1 : (con({ns}_1,m), n_2) \rightarrow (con({ns}_2,m),n_3)
        \\
     con(\{ l_1, ~\dots,~ l_k \}, m) 
        & = &  
        \bigcup ~ \{ f^{-1}(l_i) \}
        \\
\end{array} \]

@@

The goal of this section is to prove that the concretization and compilation functions commute. That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values afterwards.

@@

>>>>

\para{Syntax}

@@

  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
     \\
     \textbf{compile}( p_1, \dots, p_k ) = \\
     ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\

  \end{array} \]%

@@

\para{Compilation}

Figure~\ref{fig:abgp-syntax} also defines compilation from a \sysname policy to an ABGP policy. It starts by compiling separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$, the particular test $t_i$, and the preference ordering $ord_i$.

The function $compile_{ABGP}$ then takes tuples of $(t_i, PG_i, ord_i)$ and returns an ABGP policy. It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.

@@

Here we define what it means to concretize an abstract \sysname policy. 
Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.

\[ \begin{array}{lcl}
  con(\emptyset,\Gamma)                        & = & \emptyset \\
  con(l,\Gamma)                                & = & \Sigma ~ f^{-1}(l) \\
  con(r_1 \cup r_2,\Gamma)                     & = & con(r_1,\Gamma) \cup con(r_2,\Gamma) \\
  con(r_1 \cap r_2,\Gamma)                     & = & con(r_1,\Gamma) \cap con(r_2,\Gamma) \\
  con(!r,\Gamma)                               & = & !con(r,\Gamma) \\
  con(r^*,\Gamma)                              & = & con(r,\Gamma)^* \\
  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma)  & = & pfx \Rightarrow con(r_1,\Gamma), \dots, con(r_k,\Gamma) \\
  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma)  & = & \{ pfx \Rightarrow con(r_1,\Gamma) \cap \textbf{end}(l), \dots, \\
  & & ~~~~~~~~~~~~~~~ con(r_k,\Gamma) \cap \textbf{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
\end{array} \]

For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\textbf{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$. \textbf{Note}: we need the side condition that $\textbf{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
We can also define concretization over the ABGP policy as:

\[ \begin{array}{lcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,G) 
        & = & 
        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,G) 
        & = &  
        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,G)
        \\
     con(pfx \rightarrow {pc},\ell,\Gamma,G) 
        & = &  
        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,G)
        \\
     con(\$x \rightarrow {pc},\ell,\Gamma,G) 
        & = &  
        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
        \\
     con(ma_1, \dots, ma_k,o,\ell,\Gamma,G) 
        & = &
        con(ma_1,o,\ell,\Gamma,G), \dots, con(ma_k,o,\ell,\Gamma,G)
        \\

     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,G) 
        & = & \textbf{if}~ ns_1 = G.s ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,G),n_3)

        \\
     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,G) 
        & = &  
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
\end{array} \]

@@

The goal of this section is to prove that the concretization and compilation functions commute. That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values afterwards. First we need a few helper theorems about compilation.

@@

\subsection{Substitution}

\begin{defn}
  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
\end{defn}

\begin{thm}
  $con(compile(pol)) = compile(con(pol))$

    We know from the previous theorems and the definition of concretization, we have the following:

    \[ \begin{array}{lll}
       (t_1, PG^A_1, ord^A_1), \dots, (t_k,PG^A_k,ord^A_k)    &=& compile_{ABGP}(pol) \\
       (\Gamma(t1), PG_1, ord_1), \dots, (\Gamma(t_k),PG_k,ord_k)  &=& compile_{ABGP}(con(pol)) \\
    \end{array} \]%

    where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$, and $PG_i$ and $PG^A_i$ are related by a bisimulation induced by $f$.

  \[ \begin{array}{l}
     \textbf{compile}( (\Gamma(t_1),PG_1,ord_1), \dots, (\Gamma(t_k),PG_k,ord_k) ) = \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ \Gamma(t_i) \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord_i(M) : (in,q_n) \rightarrow (out,q_m) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG_i,m) \} \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord_i(f(m)) : (in,q_n) \rightarrow (out,q_m) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = con(\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = con(\{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = con(ord^A_i(M) : (in,q_n) \rightarrow (out,q_M)) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow con(ma) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ con(\bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \}) \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ \{ l' \rightarrow rc ~\vert~ con(rc) = \\
     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     ~~~~~ con(\{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
  \end{array} \]%

  \[ \begin{array}{l}
     = con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) )) \\
  \end{array} \]%
